Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex

\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP M(H) for a smaller horizon h.  Incrementally solving the sequence M(1), M(2) forms the basis of LR\textsuperscript{2}TDP. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value h' for which already a heuristic value V is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving M(h-1). The max-reward computation relies on knowing the maximum R\textsubscript{max} any action can yield in any state or an upper bound on it.

\subsubsection{LRTDP}
Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from s\textsubscript{0}. 
\begin{itemize}
	\item Trials start at s\textsubscript{0}
	\item Choose best action greedily in the current state based on current \emph(V)
	\item Perform  Bellman backup on the current state
	\item Sample the outcome as the chosen action
	\item Transition to the new state
	\item Repeat untill a goal, dead end or converged state is reached
	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
\end{itemize}

\subsubsection{LRTDP-FH}
Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at (\emph{s\textsubscript{0}, H}) and run for at most H time steps. A steps H steps away from s\textsubscript{0} would translate to goals in a goal-oriented MDP. However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.

\subsubsection{LR\textsuperscript{2}TDP}
LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs \emph{M(1), M(2), ... , M(H)}, in that order. It first decides how to act optimally in (s\textsubscript{0}, 1), equavalent to solving M(1) , then (s\textsubscript{0}, 2), equavalent to solving M(2), eventually solvin M(H) or running out of time halting a M(h') where h' < H. This incremental effort allows for reusing state values computed in previous states, so it memorizes all vaues and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:
 \begin{itemize}
	\item In many MDPs, the optimal policy M(h) for some h < H is near optimal for M(H), it thus may have a solution when stopped prematurely
	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
	\item It optimally memorizes a large fraction of augmented states to save memory
	\item a large fraction of state space may be unreachable from s\textsubscript{0} and it avoid storing information it does not need

	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.  
\end{itemize}

\subsubsection{GLUTTON}
Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward \emph{R\textsubscript{max}} any action can yield in a state or an upper bound on it. Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive. Glutton uses the following mechanisms to optimize for large branching factors:
\begin{itemize}
	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
	\item Seperating out Natural Dynamics: to reuse variable samples when generator succesors for multiple actions, by seperating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both. 
	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same (s, h) pair. When full, it chooses state-action pars for eviction ans replacement randomly. 
	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely. It compares the optimal action from a h' with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.  
\end{itemize}

>>>>

\subsection{Reverse Iterative Deepening for Finite-Horizon MDPs with Large Branching Factors (2012)~\cite{kolobov2012glutton}}
The IPPC-2011 introduces more realistic MDPs to accommodate real-world systems with large branching factors cause by \emph{natural dynamics} and a limited time for the planner to come up with a policy. For this reason planners needed to be scalable and sensitive to the expected reward maximization. Glutton introduces an off-line algorithm based on LR\textsuperscript{2}TDP and relies on the fact that a successful policy can be produced by solving an MDP $M(H)$ for a smaller horizon $h$. Incrementally solving the sequence $M(1)$, $M(2)$ forms the basis of LR\textsuperscript{2}TDP\@. By iterating on the distance from the horizon, data can be reused (and is stored in the cache until the hash-table is full). The max-reward heuristic finds the largest horizon value $h'$ for which already a heuristic value $V$ is estimated. The  computation time remains much lower because it runs quickly into states that converged while solving $M(h-1)$. The max-reward computation relies on knowing the maximum $R_{max}$ any action can yield in any state or an upper bound on it.

\subsubsection{LRTDP}
Using goal oriented MDPs, the \emph{Labelled Real-Time Dynamic Programmer} (LRTDP) operates a series of trials starting from $s_0$.

\begin{itemize}
	\item Trials start at $s_0$
	\item Choose best action greedily in the current state based on current $V$
	\item Perform  Bellman backup on the current state
	\item Sample the outcome as the chosen action
	\item Transition to the new state
	\item Repeat until a goal, dead end or converged state is reached
	\item After trial, special convergence check on all states in the trial is performed to prove the convergence of these values
\end{itemize}

\subsubsection{LRTDP-FH}

Adapting LRTDP to a finite horizon MDP \emph{M(H)} requires to let each trial start at ($s_0$) and run for at most H time steps. A steps $H$ steps away from $s_0$ would translate to goals in a goal-oriented MDP. However, it's anytime performance to meet the demands of a dynamic environment is not very good, creating the need for a more sophisticated approach \cite{kolobov2012glutton}.

\subsubsection{LR\textsuperscript{2}TDP}

LR\textsuperscript{2}TDP uses \emph{reverse iterative deepening} and LRTDP-FH to solve a sequence of MDPs $M(1)$, $M(2)$, \ldots , $M(H)$, in that order. It first decides how to act optimally in ($s_0$, 1), equivalent to solving M(1) , then ($s_0$, 2), equivalent to solving $M(2)$, eventually solving $M(H)$ or running out of time halting a $M(h')$ where $h' < H$. This incremental effort allows for reusing state values computed in previous states, so it memorizes all values and solves for smaller horizons by backchaining from the goal LRTDP-FH iterates over search depth while LR\textsuperscript{2}TDP iterates over the distance from the horizon and is likely to be better because:

 \begin{itemize}
	\item In many MDPs, the optimal policy $M(h)$ for some $h < H$ is near optimal for M(H), it thus may have a solution when stopped prematurely
	\item it's trials are very short because backchaining from the goal leads to a lots of convergence
	\item It optimally memorizes a large fraction of augmented states to save memory
	\item a large fraction of state space may be unreachable from $s_0$ and it avoid storing information it does not need
	\item it should however use a heuristic to treat states that has never been encountered when stopped prematurely, could be a fall back or a default action.
\end{itemize}

\subsubsection{GLUTTON}

Glutton uses the \emph{Max-Reward} heuristic that relies on knowing the maximum reward $R_{max}$ any action can yield in a state or an upper bound on it. Large branching factors induce that the computation of the Bellman Backups becomes prohibitively expensive. Glutton uses the following mechanisms to optimize for large branching factors:

\begin{itemize}
	\item Subsampling the transition function, is not enough to decrease the amount of computations yet
	\item Separating out Natural Dynamics: to reuse variable samples when generator successors for multiple actions, by separating the actions' effects into natural dynamics (\emph{exogenous}), those due to the action itself (\emph{pure effects}) and those do a mix of both.
	\item Caching the transition function samples: as LR\textsuperscript{2}TDP populates the state-value hash table lazily, Glutton uses  this memory as a cache for samples from the transition function, so it doesn't have to regenerate the action when encountering the same $(s,h)$ pair. When full, it chooses state-action pars for eviction ans replacement randomly.
	\item Default policies: Glutton uses 3 tricks to determine a policy when stopped prematurely. It compares the optimal action from a $h'$ with a simple cyclic policy or a complete random policy and chooses the best of these based on the reward.
\end{itemize}
